A Certified Interpreter for the List Machine Benchmark

### 2020-06-08 papers/SBLP2020/paper.tex
Fixed some typos.

\begin{abstract}
Formal models are an important tool in the programming languages research
community. However, such models are full of intricacies and, due to that,
they are subject to subtle errors. Such failures motivated the usage of
tools to ensure the correctness of these formalisms. One way to eliminate
such errors is to encode models in a dependently-typed language in order
to ensure ``correctness-by-construction''.

In this work, we use follow this idea to build the verified interpreter
for the list machine benchmark in the Agda programming language.
\end{abstract}

>>>>

\begin{abstract}
Formal models are important tools in the programming languages research
community. However, such models are full of intricacies and, due to that,
they are subject to subtle errors. Such failures motivated the usage of
tools to ensure the correctness of these formalisms. One way to eliminate
such errors is to encode models in a dependently-typed language in order
to ensure its ``correctness-by-construction''.

In this work, we use this idea to build a verified interpreter
for the list machine benchmark in the Agda programming language.
\end{abstract}
